Compositional equivalences based on Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-05-15 2016-Weak-FH-Bisim/WeakBisim.tex
Proofs

For the sake of simplicity, we prove the rule in the  restricted case where $n$ and $m$ to be equal to $1$, hence a single tau open transition will be considered on each side of the potentially visible one. The proof may be easily generalized to the multiple tau open transitions by using the same reasoning and (\WTTrois)~rule. Consider each open transition separately:
\begin{enumerate}
\item For the first open transition in $\mathcal{T}_1$:
\begin{mathpar}
%\inferrule{
 \openrule
    {
       \beta_{1j}^{j\in J_1'},\Pred_1,\Post_1   }
         {s_{10} \OTarrow {\tau} s_{11}}          
\end{mathpar}
we have $(s,t|\Pred_{s,t})\in\mathcal{R}$ by hypothesis and $s=s_{10}$. Thus, by  Definition \ref{def-Weak-bisim} we  can deduce there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {u \OTWeakarrow {\alpha_x} u_x}
\end{mathpar}
 such that  $\forall x,J_{x}=\{j\in J_1'|\beta_{1j}\neq\tau\}, u=t,  (s_{11},t_x|\Pred_{s_{11},u_x})\in \mathcal{R}$ and \\
 $\Pred_{s,t} \land \Pred_1\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}}
  \!\! \left( \forall j\in J_x.\vis{\beta_{1j}}=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
     \land \alpha_x\!=\!\tau \land  
     \Pred_{s_{11},u_x}\subst{\Post_1\uplus\Post_{OT_x}}\right)$

Note that, because $\AlgE\cap\AlgA=\emptyset$  (actions and expressions are disjoint) and $\alpha_x\!=\!\tau$ we have 
directly ($\alpha_x$ cannot be a variable, and cannot contain expressions/variables because $\tau$ has no parameter):
\begin{mathpar}
    \openrule
         {
           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {u \OTWeakarrow {\tau} u_x}
\end{mathpar}
\item Concerning the middle open transition in $\mathcal{T}_1$:
 \begin{mathpar}
     \openrule
         {
           \beta_{2j}^{j \in J_2'},\Pred_2,\Post_2 }
         {s_{20} \OTarrow {\alpha} s_{21}} 
\end{mathpar}
we have  $(s_{11},u_x|\Pred_{s_{11},u_x})\in \mathcal{R}$  and $s_{11}=s_{20}$. Again 
 by Definition \ref{def-Weak-bisim} we can deduce there exist weak open transitions $\symb{WOT}_{y}^{y\in Y} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{y}^{j\in J_{y}}, \Pred_{OT_{y}},\Post_{OT_{y}}}
         {u_x \OTWeakarrow {\alpha_{y}} v_{y}}
\end{mathpar}
 such that  $\forall y, J_{y}=\{j\in J_2'|\beta_{2j}\neq\tau\}, 
(s_{21},v_{y}|\Pred_{s_{21},v_{y}})\in \mathcal{R}$; \\
 $\Pred_{s_{11},u_x} \land \Pred_2\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{y\in Y}}
 \!\!  \left( \forall j\in J_{y}. \vis{\beta_{2j}}\!=\!\gamma_{jy}\Rightarrow \Pred_{OT_{y}}\!\land \alpha\!=\!\alpha_{y} \land  
     \Pred_{s_{21},v_{y}}\subst{\Post_2\uplus\Post_{OT_{y}}}\right)$

\item Similarly to the case 1,  the third  open transition in $\mathcal{T}_1$:
     \begin{mathpar}
%\inferrule{
 \openrule
    {
       \beta_{3j}^{j \in J_3'},\Pred_3,\Post_3   }
         {s_{30} \OTarrow {\tau} s_{31}} \in \mathcal{T}          
\end{mathpar}
From previous case, we have $(s_{21},v_{y}|\Pred_{s_{21},v_{y}})\in \mathcal{R}$, and we have $s_{21}=s_{30}$. Then, by
 Definition \ref{def-Weak-bisim} there exist weak open transition $\symb{WOT}_{x}^{z\in Z} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{jz}^{j\in J_{z}}, \Pred_{OT_{z}},\Post_{OT_{z}}}
         {v_{y} \OTWeakarrow {\tau} w_{z}}
\end{mathpar}
 such that  $\forall z, J_{z}= \{j\in J_3'|\beta_{3j}\neq\tau\}, 
(s_{31},w_{z}|\Pred_{s_{31},w_{z}})\in \mathcal{R}$,  $w_z=t_x$ and \\
 $\Pred_{s_{21},v_{y}} \land \Pred_3\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{z\in Z}}
   \!\left( \forall j\in J_{z}. \vis{\beta_{3j}}\!=\!\gamma_{jz} \! \Rightarrow\! \Pred_{OT_{z}}\!
     \land\! \alpha_{z}\!=\!\tau \land  
     \Pred_{s_{31},t_{x}}\subst{\Post_3\uplus\Post_{OT_{z}}}\right)$

@@

\begin{mathpar}
  \mprset {vskip=.5ex}
\inferrule {
\openrule
         {
           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTWeakarrow {\tau} u_x}
\qquad
\openrule
         {
           \gamma_{j y}^{j\in J_{y}}, \Pred_{OT_{ y}},\Post_{OT_{y}}}
         {u_x \OTWeakarrow {\alpha_{y}} v_{y}}
\qquad
\openrule
         {
           \gamma_{jz}^{j\in J_{z}}, \Pred_{OT_{z}}, \Post_{OT_{z}}}
         {v_{y} \OTWeakarrow {\tau} t_{x}}
\\ 
\set{\gamma'}=\gamma_{j x}^{j\in J_{x}} \dotcup \gamma_{j x y}^{j\in J_{x y}} \subst{\Post_{OT_x}} \dotcup\gamma_{j x y z}^{j\in J_{x y z}} \subst{\Post_{OT_{x y}}\shortotimes\Post_{OT_x}}\\
\Pred=\Pred_{OT_x}\land\Pred_{OT_{x y}}\subst{\Post_{OT_x}}\land \Pred_{OT_{x y z}}\subst{\Post_{OT_{x y}}\shortotimes\Post_{OT_x}}\\
\Post= \Post_{OT_{x y z}} \shortotimes \Post_{OT_{x y}}\shortotimes\Post_{OT_{x}}\quad \alpha'_{x y}=\alpha_{y}\subst{\Post_{OT_x}}\\
}
{
\openrule
         {
           \set{\gamma},
		\Pred, \Post}  
         {t \OTWeakarrow {\alpha'_{y}} t_{x}} 
} 
 \end{mathpar}
So we need to prove that the following statement holds:\\
$\Pred_{s,t} \land \Pred\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}} \displaystyle{\bigvee_{y\in Y}}\displaystyle{\bigvee_{z\in Z}}
   ( \forall j\in J. \gamma_j'=\gamma_{j}  \Rightarrow \Pred
     \land \alpha \!=\! \alpha_{y}' \land  
     \Pred_{s',t_{x}}\subst{\Post_{OT}\uplus\Post\,})$

Let's start with the hypothesis we have:\\

@@

 \! \! \left( \forall j\in J_x. \vis{\beta_{1j}}=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
     \land \alpha_x\!=\!\tau \land  
     \Pred_{s_{11},t_x}\subst{\Post_1\uplus\Post_{OT_x}}\right)$\\

@@

  \!\! \left( \forall j\in J_x. \vis{\beta_{1j}}=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
     \land \alpha_x\!=\!\tau \land  
     \Pred_{s_{11},t_x}\subst{\Post_1\uplus\Post_{OT_x}}\right) \wedge\Pred_2\subst{\Post_1\uplus\Post_{OT_x}}  \\

@@

\!\!   \left(\forall j\in J_x. \vis{\beta_{1j}}\!=\!\gamma_{jx}\Rightarrow \Pred_{OT_x}
     \!\land\! \alpha_x\!=\!\tau\land(\Pred_{s_{11},t_x}\wedge\Pred_2)\subst{\Post_1\uplus\Post_{OT_x}} \right)$\\
By replacing the inner sub-term $(\Pred_{s_{11},t_x}\wedge\Pred_2)$ by the conclusion of the  implication given in case 2,  the formula becomes: \\

@@

   \!\!(\forall j\in J_x. \vis{\beta_{1j}}\!\!=\!\gamma_{jx}  \Rightarrow \Pred_{OT_x}
     \land \alpha_x\!=\!\tau \land\Big(\displaystyle{\bigvee_{y\in Y}}(
    \forall j\in J_{y}. \vis{\beta_{2j}}\!=\!\gamma_{jy} \\ \Rightarrow \Pred_{OT_{y}}\land \alpha'\!=\!\alpha_{y}\! \land \Pred_{s_{21},t_{y}'}\subst{\Post_2\uplus\Post_{OT_{y}}}\Big)\subst{\Post_1\uplus\Post_{OT_x}})$\\

@@

(\forall j\in J_x. \vis{\beta_{1j}}\!\!=\!\gamma_{jx} \land  \forall j \in J_{y}. (\vis{\beta_{2j}}\!=\!\gamma_{jy})\subst{\Post_1\uplus\Post_{OT_x}}   \Rightarrow\Pred_{OT_x} \land  \Pred_{OT_{x y}} \subst{\Post_1\uplus\Post_{OT_x}} \land \alpha_x\!=\!\tau \land (\alpha'\!=\!\alpha_{y}) \subst{\Post_1\uplus\Post_{OT_x}} \land \Pred_{s_{21},t_{y}'}\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{y}}\shortotimes \Post_{OT_x}})$\\ 
As $Post_1$  does not act on $\gamma_{jy}$, nor on $ \Pred_{OT_{y}}$ and $  \alpha_{y}$, as well $\Post_{OT_x}$  does not act on $\alpha'$, nor on  $\beta_{2j}$ the formula can be simplified as follows:\\

@@

(\forall j\in J_x. \vis{\beta_{1j}}\!=\!\gamma_{jx} \land  \forall j \in J_{y}. \vis{\beta_{2j}}\subst{\Post_1}=\gamma_{jy} \subst{\Post_{OT_x}}  \Rightarrow\Pred_{OT_x} \land  \Pred_{OT_{y}} \subst{\Post_{OT_x}} \land \alpha_x =\tau \land \alpha'\subst{\Post_1}=\alpha_{y} \subst{\Post_{OT_x}} \land \Pred_{s_{21},t_{y}'}\\\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{y}}\shortotimes \Post_{OT_x}})$\\ 

@@

\Big(\forall j\in J_x.\vis{\beta^1_j}\!=\!\gamma_{jx} \land  \forall j \in J_{y}. \vis{\beta_{2j}}\subst{\Post_1}\!=\!\gamma_{jy} \subst{\Post_{OT_x}}\Rightarrow \Pred_{OT_x}\land\Pred_{OT_{y}}\subst{\Post_{OT_x}} \land \alpha_x=\tau \land \alpha'\subst{\Post_1}= \alpha_{y} \subst{\Post_{OT_x}} \land \\(\Pred_{s_{21},t_{y}'} \land  \Pred_3) \subst{\Post_2\shortotimes \Post_1\uplus \Post_{OT_{y}}\shortotimes\Post_{OT_x}})$\\ 
Again note that because of the domain independence of the substitution, we removed $\Post_1$ and  we  added the term $\Post_{OT_{y}}\shortotimes\,\Post_{OT_x}$ in the substitution of the right side of the implication.\\
Finally, by replacing the predicate $(\Pred_{s_{21},t_{y}} \land  \Pred_3)$

@@

$(\Pred_{s,t} \land \Pred_1)\land \Pred_2\subst{\Post_1} \land \Pred_3\subst{\Post_2\shortotimes\Post_1}\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}} \displaystyle{\bigvee_{y\in Y}} \displaystyle{\bigvee_{z\in Z}} 
\Big(\forall\! j\in\! J_x.\vis{\beta_{1j}}\!=\!\gamma_{jx} \land  \forall j \!\in\! J_{y}.\vis{\beta_{2j}\subst{\Post_{OT_x}}}\!=\!\gamma_{jy} \subst{\Post_{OT_x}}  \land 
 \forall j\!\in\! J_{z}. \vis{\beta_{3j} \subst{\Post_2\,\shortotimes\,\Post_1}} \!=\!\gamma_{jz} \subst{\Post_{OT_{y}}\shortotimes\Post_{OT_x}}  \Rightarrow  \Pred_{OT_x}\land\Pred_{OT_{y}} \subst{\Post_{OT_x}} \land\\ 
  \Pred_{OT_{z}}\subst{\Post_{OT_{y}}\shortotimes\Post_{OT_x}} \land \alpha_x\!=\!
\tau \land \alpha'\subst{\Post_1}=\alpha_{y} \subst{\Post_{OT_x}}\land \alpha_{z}\!=\!\tau \land \Pred_{s_{31},t_{z}}  \subst{\underbrace{\Post_3\shortotimes\Post_2\shortotimes\Post_1}_{\Post_{OT}}\uplus \underbrace{\Post_{OT_{z}}\shortotimes \Post_{OT_{y}}\shortotimes\Post_{OT_x}}_{\Post}} \Big)$\\
Having $s_{31}=s'$ and $\alpha= \alpha'\subst{\Post_1}$ and rewriting the formula:\\ 

@@

\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}} \displaystyle{\bigvee_{y\in Y}} \displaystyle{\bigvee_{z\in Z}} 
(\forall j\in J. \vis{\beta_{1j}}\dotcup \vis{\beta_{2j}\subst{\Post_{OT_x}}}\dotcup \vis{\beta_{3j} \subst{\Post_2\,\shortotimes\,\Post_1}}=\\\gamma_{j x} \dotcup \gamma_{jy} \subst{\Post_{OT_x}}  \dotcup \gamma_{jz} \subst{\Post_{OT_{y}}\shortotimes\Post_{OT_x}} \Rightarrow  \Pred \land \alpha_x=
\tau \land \alpha =\alpha_{y}\subst{\Post_{OT_x}} \land\\ \alpha_{z}=\tau \land \Pred_{s',t_{x}}\subst{\Post_{OT}\uplus\Post\,}$\\
we can conclude:\\
 This is exactly what we needed to prove \TODO{je dois generaliser}. \qed

@@

$\forall p \in [0..(n_1\!+\!n_2\!+\!2)]\,\, Q\models{\openrule
			{
				(\beta_{pj})^{j\in J\cap\Holes(Q)}, {{\Pred''_p}},  
				{{\Post''_p}}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\alpha_{p}}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
$ 
In this equation, and using cases 1, 2 and 3 above, we have for all $k\in [0\ldots n_1+n_2+2]$, $\beta_{kj_0}=\alpha_k$.

>>>>

For the sake of simplicity, we prove the rule in the  restricted case where $n$ and $m$ to be equal to $1$, hence a single tau open transition will be considered on each side of the potentially visible one. The proof may be easily generalized to the multiple tau open transitions by using the same reasoning and (\WTTrois)~rule. Consider each open transition separately:
\begin{enumerate}
\item For the first open transition in $\mathcal{T}_1$:
\begin{mathpar}
%\inferrule{
 \openrule
    {
       \beta_{1j}^{j\in J_1'},\Pred_1,\Post_1   }
         {s_{10} \OTarrow {\tau} s_{11}}          
\end{mathpar}
by hypothesis we have $(s,t|\Pred_{s,t})\in\mathcal{R}$  and $s=s_{10}$. Thus, by  Definition \ref{def-Weak-bisim} we  can deduce there exist weak open transitions $\symb{WOT}_a^{a\in A} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j a}^{j\in J_{a}}, \Pred_{OT_a},\Post_{OT_a}}
         {u \OTWeakarrow {\alpha_1} u_a}
\end{mathpar}
 such that  $\forall a, J_{a}=\{j\in J_1'|\beta_{1j}\neq\tau\}, u=t,  (s_{11},t_a|\Pred_{s_{11},u_a})\in \mathcal{R}$ and \\
 $\Pred_{s,t} \land \Pred_1\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{a\in A}}
  \!\! \left( \forall j\in J_a.\vis{\beta_{1j}}=\gamma_{ja}  \Rightarrow \Pred_{OT_a}
     \land \alpha_1\!=\!\tau \land  
     \Pred_{s_{11},u_a}\subst{\Post_1\uplus\Post_{OT_a}}\right)$

Note that, because $\AlgE\cap\AlgA=\emptyset$  (actions and expressions are disjoint) and $\alpha_x\!=\!\tau$ we have 
directly ($\alpha_a$ cannot be a variable, and cannot contain expressions/variables because $\tau$ has no parameter):
\begin{mathpar}
    \openrule
         {
           \gamma_{j a}^{j\in J_{a}}, \Pred_{OT_a},\Post_{OT_a}}
         {u \OTWeakarrow {\tau} u_a}
\end{mathpar}
and//
$\Pred_{s,t} \land \Pred_1\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{a\in A}}
  \!\! \left( \forall j\in J_a.\vis{\beta_{1j}}=\gamma_{ja}  \Rightarrow \Pred_{OT_a}
     \land    \Pred_{s_{11},u_a}\subst{\Post_1\uplus\Post_{OT_a}}\right)$

\item Concerning the middle open transition in $\mathcal{T}_1$:
 \begin{mathpar}
     \openrule
         {
           \beta_{2j}^{j \in J_2'},\Pred_2,\Post_2 }
         {s_{20} \OTarrow {\alpha'} s_{21}} 
\end{mathpar}
we have  $(s_{11},u_a|\Pred_{s_{11},u_a})\in \mathcal{R}$  and $s_{11}=s_{20}$. Again 
 by Definition \ref{def-Weak-bisim} we can deduce there exist weak open transitions $\symb{WOT}_{b}^{b\in B} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{b}^{j\in J_{b}}, \Pred_{OT_{b}},\Post_{OT_{b}}}
         {u_a \OTWeakarrow {\alpha_{2}} v_{b}}
\end{mathpar}
 such that  $\forall b, J_{b}=\{j\in J_2'|\beta_{2j}\neq\tau\}, 
(s_{21},v_{y}|\Pred_{s_{21},v_{y}})\in \mathcal{R}$; \\
 $\Pred_{s_{11},u_a} \land \Pred_2\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{b\in B}}
 \!\!  \left( \forall j\in J_{b}. \vis{\beta_{2j}}\!=\!\gamma_{jb}\Rightarrow \Pred_{OT_{b}}\!\land \alpha'\!=\!\alpha_{2} \land  
     \Pred_{s_{21},v_{b}}\subst{\Post_2\uplus\Post_{OT_{b}}}\right)$

\item Similarly to the case 1,  the third  open transition in $\mathcal{T}_1$:
     \begin{mathpar}
%\inferrule{
 \openrule
    {
       \beta_{3j}^{j \in J_3'},\Pred_3,\Post_3   }
         {s_{30} \OTarrow {\tau} s_{31}} \in \mathcal{T}          
\end{mathpar}
From previous case, we have $(s_{21},v_{b}|\Pred_{s_{21},v_{b}})\in \mathcal{R}$, and we have $s_{21}=s_{30}$. Then, by
 Definition \ref{def-Weak-bisim} there exist weak open transition $\symb{WOT}_{a}^{c\in C} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{jc}^{j\in J_{c}}, \Pred_{OT_{c}},\Post_{OT_{c}}}
         {v_{b} \OTWeakarrow {\tau} w_{c}}
\end{mathpar}
 such that  $\forall c, J_{c}= \{j\in J_3'|\beta_{3j}\neq\tau\}, 
(s_{31},w_{c}|\Pred_{s_{31},w_{c}})\in \mathcal{R}$ and \\
 $\Pred_{s_{21},v_{b}} \land \Pred_3\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{c\in C}}
   \!\left( \forall j\in J_{c}. \vis{\beta_{3j}}\!=\!\gamma_{jc} \! \Rightarrow\! \Pred_{OT_{c}}\!
     \land\!  
     \Pred_{s_{31},w_{c}}\subst{\Post_3\uplus\Post_{OT_{c}}}\right)$

@@

\begin{mathpar}
  \mprset {vskip=.5ex}
\inferrule {
\openrule
         {
           \gamma_{j a}^{j\in J_{a}}, \Pred_{OT_x},\Post_{OT_a}}
         {t \OTWeakarrow {\tau} u_a}
\qquad
\openrule
         {
           \gamma_{j b}^{j\in J_{b}}, \Pred_{OT_{ y}},\Post_{OT_{b}}}
         {u_a \OTWeakarrow {\alpha_2} v_{b}}
\qquad
\openrule
         {
           \gamma_{jc}^{j\in J_{c}}, \Pred_{OT_{c}}, \Post_{OT_{c}}}
         {v_{b} \OTWeakarrow {\tau} w_{c}}
\\ 
\set{\gamma'}=\gamma_{j a}^{j\in J_{a}} \dotcup \gamma_{j a b}^{j\in J_{b}} \subst{\Post_{OT_a}} \dotcup\gamma_{jc}^{j\in J_{c}} \subst{\Post_{OT_{ b}}\shortotimes\Post_{OT_a}}\\
\Pred=\Pred_{OT_a}\land\Pred_{OT_{b}}\subst{\Post_{OT_a}}\land \Pred_{OT_{c}}\subst{\Post_{OT_{b}}\shortotimes\Post_{OT_a}}\\
\Post= \Post_{OT_{c}} \shortotimes \Post_{OT_{b}}\shortotimes\Post_{OT_{a}}\quad \alpha''=\alpha_{2}\subst{\Post_{OT_a}}\\
}
{
\openrule
         {
           \set{\gamma},
		\Pred, \Post}  
         {u \OTWeakarrow {\alpha''} w_{c}} 
} 
 \end{mathpar}
So need to prove that the following statement holds:\\
$\Pred_{s,t} \land \Pred\\
  ( \forall j\in J. \gamma_j'=\gamma_{j}  \Rightarrow \Pred
     \land \alpha \!=\! \alpha'' \land  
     \Pred_{s',t_{x}}\subst{\Post_{OT}\uplus\Post\,})$\\
     Let's start with the hypothesis and consider  $u=t$   we have:\\

@@

\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{a\in A}}
 \! \! \left( \forall j\in J_a. \vis{\beta_{1j}}=\gamma_{ja}  \Rightarrow \Pred_{OT_a}
      \land  
     \Pred_{s_{11},u_a}\subst{\Post_1\uplus\Post_{OT_a}}\right)$\\

@@

 \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{a\in A}}
  \!\! ( \forall j\in J_a. \vis{\beta_{1j}}=\gamma_{ja}  \Rightarrow \Pred_{OT_a} \land
     \Pred_{s_{11},u_a}\subst{\Post_1\uplus\Post_{OT_a}}) \wedge\\ \Pred_2\subst{\Post_1\uplus\Post_{OT_a}}  \\

@@

 \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{a\in A}}
\!\!   \left(\forall j\in J_a. \vis{\beta_{1j}}\!=\!\gamma_{ja}\Rightarrow \Pred_{OT_a}
     \!\land(\Pred_{s_{11},u_a}\wedge\Pred_2)\subst{\Post_1\uplus\Post_{OT_a}} \right)$\\
By replacing the inner predicate $(\Pred_{s_{11},u_a}\wedge\Pred_2)$ by the conclusion of the  statement given in case 2,  the formula becomes: \\

@@

 \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{a\in A}}
   \!\!(\forall j\in J_a. \vis{\beta_{1j}}\!\!=\!\gamma_{ja}  \Rightarrow \Pred_{OT_a}
      \land (\displaystyle{\bigvee_{b\in B}}(
    \forall j\in J_{b}. \vis{\beta_{2j}}\!=\!\gamma_{jb}  \Rightarrow \Pred_{OT_{b}}\land \alpha'\!=\!\alpha_2\! \land \Pred_{s_{21},v_{b}}\subst{\Post_2\uplus\Post_{OT_{b}}})\subst{\Post_1\uplus\Post_{OT_a}})$\\

@@

\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{a\in A}}\, \displaystyle{\bigvee_{b\in B}} 
(\forall j\in J_a. \vis{\beta_{1j}}\!\!=\!\gamma_{ja} \land  \forall j \in J_{b}. (\vis{\beta_{2j}}\!=\!\gamma_{jb})\subst{\Post_1\uplus\Post_{OT_a}}   \Rightarrow\Pred_{OT_a} \land  \Pred_{OT_{b}} \subst{\Post_1\uplus\Post_{OT_a}} \land  (\alpha'\!=\!\alpha_{2}) \subst{\Post_1\uplus\Post_{OT_a}} \land \\ \Pred_{s_{21},v_{b}}\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{b}}\shortotimes \Post_{OT_a}})$\\ 
Since $Post_1$  does not act on $\gamma_{jb}$, nor on $ \Pred_{OT_{b}}$ and $  \alpha_{2}$, as well $\Post_{OT_a}$  does not act on $\alpha'$, nor on  $\beta_{2j}$ the formula can be simplified as follows:\\

@@

\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{a\in A}}\, \displaystyle{\bigvee_{b\in B}} 
(\forall j\in J_a. \vis{\beta_{1j}}\!=\!\gamma_{ja} \land  \forall j \in J_{b}. \vis{\beta_{2j}}\subst{\Post_1}=\gamma_{jb} \subst{\Post_{OT_a}}  \Rightarrow\Pred_{OT_a} \land  \Pred_{OT_{b}} \subst{\Post_{OT_a}} \land \alpha'\subst{\Post_1}=\alpha_{2} \subst{\Post_{OT_a}} \land \Pred_{s_{21},v_b}\\\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{b}}\shortotimes \Post_{OT_a}})$\\ 

@@

(\forall j\in J_a.\vis{\beta^1_j}\!=\!\gamma_{ja} \land  \forall j \in J_{b}. \vis{\beta_{2j}}\subst{\Post_1}\!=\!\gamma_{jb} \subst{\Post_{OT_a}}\Rightarrow \Pred_{OT_a}\land\Pred_{OT_{b}}\subst{\Post_{OT_a}} \land  \alpha'\subst{\Post_1}= \alpha_{2} \subst{\Post_{OT_a}} \land (\Pred_{s_{21},v_b} \land  \Pred_3)\\ \subst{\Post_2\shortotimes \Post_1\uplus \Post_{OT_{b}}\shortotimes\Post_{OT_a}})$\\ 
Again note that because of the domain independence of the substitution, we removed $\Post_1$ and  we  added the term $\Post_{OT_{b}}\shortotimes\,\Post_{OT_a}$ in the substitution of the right side of the implication.\\
Finally, by replacing the predicate $(\Pred_{s_{21},v_{b}} \land  \Pred_3)$

@@

$\Pred_{s,t} \land \underbrace{\Pred_1\land \Pred_2\subst{\Post_1} \land \Pred_3\subst{\Post_2\shortotimes\Post_1}}_{\Pred_{OT}}\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{a\in A}}\, \displaystyle{\bigvee_{b\in B}}\, \displaystyle{\bigvee_{c\in C}} 
(\forall\! j\in\! J_a.\vis{\beta_{1j}}\!=\!\gamma_{ja} \land  \forall j \!\in\! J_{b}.\vis{\beta_{2j}\subst{\Post_{OT_a}}}\!=\!\gamma_{jb} \subst{\Post_{OT_a}}  \land 
 \forall j\!\in\! J_{c}. \vis{\beta_{3j} \subst{\Post_2\,\shortotimes\,\Post_1}} \!=\!\gamma_{jc} \subst{\Post_{OT_{b}}\shortotimes\Post_{OT_a}}  \Rightarrow\\
   \underbrace{\Pred_{OT_a}\land\Pred_{OT_{b}} \subst{\Post_{OT_a}} \land 
  \Pred_{OT_{c}}\subst{\Post_{OT_{b}}\shortotimes\Post_{OT_a}}}_{\Pred} \land  \underbrace{\alpha'\subst{\Post_1}}_{\alpha}=\underbrace{\alpha_{2} \subst{\Post_{OT_a}}}_{\alpha''} \land\\ \Pred_{s_{31},w_{c}}  \subst{\underbrace{\Post_3\shortotimes\Post_2\shortotimes\Post_1}_{\Post_{OT}}\uplus \underbrace{\Post_{OT_{c}}\shortotimes \Post_{OT_{b}}\shortotimes\Post_{OT_a}}_{\Post}})$\\
 \TODO{Comment passer a ca?}\\
$\forall j\in J_a\uplus J_b\uplus J_c. \vis{\beta_{1j}}\dotcup \vis{\beta_{2j}\subst{\Post_{OT_a}}}\dotcup \vis{\beta_{3j} \subst{\Post_2\,\shortotimes\,\Post_1}}=\gamma_{j a} \dotcup \gamma_{jb} \subst{\Post_{OT_a}}  \dotcup \gamma_{jc} \subst{\Post_{OT_{b}}\shortotimes\Post_{OT_a}}
$ \\
We have  $s_{31}=s'$, so can rewrite the formula:\\

@@

\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{a\in A}} \displaystyle{\bigvee_{b\in B}} \displaystyle{\bigvee_{c\in C}} 
(\forall j\in J.\gamma_j'=\gamma_j \Rightarrow  \Pred \land \alpha=\alpha''  \land \Pred_{s',w_{c}}\subst{\Post_{OT}\uplus\Post\,}$\\
Thus, we can conclude: \TODO{que dire pour passer ici}\\
(\forall j\in J.\gamma_j'=\gamma_j \Rightarrow  \Pred \land \alpha=\alpha''  \land \Pred_{s',t_{x}}\subst{\Post_{OT}\uplus\Post\,}$\\
 This is exactly what we needed to prove. \qed

@@

$\forall p \in [0..(n_1\!+\!n_2\!+\!2)]\,\, Q\models{\openrule
			{
				(\beta_{pj})^{j\in J\cap\Holes(Q)}, {{\Pred''_p}},  
				{{\Post''_p}}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\alpha_{p}}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
$\\ 
In this equation, and using cases 1, 2 and 3 above, we have for all $k\in [0\ldots n_1+n_2+2]$, $\beta_{kj_0}=\alpha_k$.
